\documentclass{article}
\begin{document}
\section*{1.2.1}
\label{sec:1_2_1}

5 : establishing dq(dA) and dA.

5 : writing down the distance between the charge and the field point.

5 : symmetry argument / cancellation of the field components (vector r)

5 : right answer

Had proper charge distribution (not dA) and decent symmetry argument.
Net: I would have awarded less (7 instead of 10). Grade (same): 10/30.

\section*{2.1.2}
\label{sec:2_1_2}

5 : proper Maclaurin expansion

5 : proper analysis after substitution

Did a proper Maclaurin series expansion. Would have been hard to analyze,
though.
Net: +1 (3/10).

\section*{2.2.1}
\label{sec:2_2_1}

5 : establishing dq(dV) and dV.

5 : writing down the distance between the charge and the field point.

5 : symmetry argument / cancellation of the field components (vector r)

5 : right answer

Had proper charge distribution and proper distance between charge and field
point.

Net: +2 (7/40)

\section*{3.1.1}
\label{sec:3_1_1}

5: Demonstrate that $ Q_{enc} = 0 $ does not imply that $ E = 0 $.

5: Right answer.

I would have awarded 0 points. The student should still receive 3/30.

\section*{3.4.1.a}
\label{sec:3_4_1_a}

Do the math properly.

+4.

\section*{3.4.1.b}
\label{sec:3_4_1_b}

Do the math properly. Should have the same answer as 3.4.1.a. If not the same,
then zero points.

+1: Sign error.

5/30.

\section*{4.2.2}
\label{sec:4_2_2}

4 : Having del in spherical coordinates and picking off the right components.
3 : Having the right answer

Confused gradient operator with divergence operator in spherical coordinates. +2
(16/20).

\section*{5.1.1}
\label{sec:5_1_1}

5 : proper $ \rho dV $
5 : proper distance from charge
5 : proper symmetry argument and right answer

\section*{5.1.2}
\label{sec:5_1_2}

5 : proper sign and bounds on integral
5 : proper integrand
5 : right answer

+9. Good continuous potential. 10/30.

\section*{5.3.1}
\label{sec:5_3_1}

5 : Picking proper Gaussian surface (cylinder)
5 : Choosing the integral to be over some finite length
5 : Having the right integrand and integral

Good work. 30/30.

\section*{5.4}
\label{sec:5_4}

10 : Knowing what it means to calculate a dipole moment.
10 : Writing the integral over one line in terms of this calculation.
10 : Having the right answer including both lines.

+5 (20/30). Good knowledge of superposition.

\section*{ME.2}
\label{sec:me_2}

5/10.

\section*{ME.3}
\label{sec:me_3}

Didn't understand Gauss' law.

\section*{ME.4}
\label{sec:me_4}

10/10. Did great work. Got the right answer.

\section*{ME.5}
\label{sec:me_5}

10/10.

\section*{ME.6}
\label{sec:me_6}



\end{document}
